%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
  {Sr. Software Engineer} % Job title
  {Philips Respironics} % Organization
  {Pittsburgh, Pennsylvania} % Location
  {March 2022 - Present} % Date(s)
  {
    \begin{cvitems}
    \item
    {
      \href{https://www.usa.philips.com/healthcare/product/HC0055500/trilogy-evo-portable-hospital-to-home-ventilator}{\color{RoyalBlue}Trilogy Evo/EV300}
      \begin{itemize}
        \item Created a custom layer and set of recipes to facilitate a migration to a Yocto based custom Linux distribution.
        \item Led a team of 5 members to release software in accordance with IEC 62304 for a class C ventilator.
        \item Refactored cryptographic library to leverage dependency injection to increase testability and reduce coupling.
        \item Facilitated and hosted agile ceremonies.
      \end{itemize}
    }
    \end{cvitems}
  }

\cventry
  {Software Engineer} % Job title
  {Philips Respironics} % Organization
  {Pittsburgh, Pennsylvania} % Location
  {August 2017 - March 2022} % Date(s)
  {
    \begin{cvitems}
    \item
    {
      \href{https://www.usa.philips.com/healthcare/product/HC0055500/trilogy-evo-portable-hospital-to-home-ventilator}{\color{RoyalBlue}Trilogy Evo/EV300}
      \begin{itemize}
        \item Worked alongside a group of 10 team members to develop, test, and deploy software for a multi-processor class C ventilator.
        \item Created a serial data passthrough mechanism to simultaneously support proprietary communication and a CO2 monitor.
        \item Designed and implemented an authentication mechanism for proprietary serial communication.
        \item Integrated third-party touchscreen driver in custom Linux BSP.
        \item Implemented PNG-based screenshot mechanism to support automated testing.
        \item Designed cryptographic hardware wrapper mechanism and derived cryptographic workflows.
        \item Maintained CI/CD job configurations and adopted Coverity static code analysis.
        \item Designed an authenticated and encrypted software upgrade scheme using the ECDSA and AES algorithms.
        \item Automated eMMC image creation with Bash script for quick functional circuit test turnaround.
      \end{itemize}
    }
    \item
    {
      \href{https://www.usa.philips.com/healthcare/product/HCNOCTN350/simplygo-mini-portable-oxygen-concentrator-poc}{\color{RoyalBlue}Next Gen Simply Go}
      \begin{itemize}
        \item Collaborated with third-party vendor to create a cryptographic hardware provisioning scheme.
        \item Documented and designed cryptographic workflows using security hardware.
      \end{itemize} 
    }
    \item
    {
      {Manufacturing Support Camera Capture Project}
      \begin{itemize}
        \item Designed cryptographic signing mechanism using a certificate chain of trust and ECDSA.
        \item Explored and implemented IoC paradigms using a dependency injection container.
        \item Leveraged DirectShow to interface with the settings and video stream of a document scanner.
        \item Added functionality to interact with an SQLite database to support local information caching.
      \end{itemize}
    }
    \item
    {
      {DevOps Initiative}
      \begin{itemize}
        \item Installed and configured Artifactory on an AWS EC2 instance using an S3 container for artifact storage.
        \item Coordinated with internal customers to resolve issues surrounding several supported server platforms.
      \end{itemize}
    }
    \end{cvitems}
  }
%---------------------------------------------------------
\end{cventries}
